{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
get reference in last paragraph right

The proof that this definition fulfills the properties from \nameref{sec:soundness} and all other
proofs can be found in the full version of the paper. \todo{cite the full version}

>>>>

The proof that this definition fulfills the properties from section \ref{sec:soundness} and all other
proofs can be found in the full version of the paper. \todo{cite the full version}
